The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-04-08 manuscript/manuscript.qmd
MS minor editting
I kept the notes you put - to delete later

In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020;@ChaudhryHeiss:] (*to add citation*) The manifestation of such trend is rolling up laws that restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs. The purpose of this study is to empirically examine how the ONGO law has impacted INGO's presence as well as the operational space after the law took effect. By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we will be able to see a more comprehensive picture of the operational space for INGOs. It will also inform as the evolving theorization of the "closing space" and dual attitudes towards INGOs hold true for an Authoritarian jurisdiction such as China.

@@

Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011]. They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees. However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs. Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021]. Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investers' right to investment return.

@@

The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs (Chaudhry & Heiss, 2018; Toepler, Zimmer, Fröhlich, & Obuch, 2020). Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for ONGOs operating in China (Feng, 2017; Hsu & Teets, 2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A couple of studies (Jia, 2017; Ye & Huang, 2018) conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.

@@

## Literature on differenciated attitudes towards INGOs (*maybe merge with literature on implementation*)

@@

## Work Field Coding notes

**Decided by how the work fields of registered NGO ROs cluster**

@@

to add

@@

We use

>>>>

In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020;@ChaudhryHeiss:2020] (*to add citation*) The manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs. The purpose of this study is to empirically examine how the ONGO law has impacted INGO's presence as well as the operational space after the law took effect. By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we will be able to see a more comprehensive picture of the operational space for INGOs. It will also inform as the evolving theorization of the "closing space" and dual attitudes towards INGOs hold true for an Authoritarian jurisdiction such as China.

@@

Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011]. They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees. However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs. Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021]. Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investers' right to investment return.

@@

- on how Chinese ONGO Law is seen as part of this trend

The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss2022; @Carothers:2016]. (*to update*) Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for ONGOs operating in China [@Feng:2017;@TeetsHsu:2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A couple of studies [@Jia2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.

@@

## Literature on differenciated attitudes towards INGOs (*maybe merge with literature on implementation?*)

@@

Based on the issue areas listed by the ONGO Law and how the work fields of registered NGO ROs cluster**

@@

This variable is derived the time difference between ROs' registration date and January 1, 2017 when the law took effect. The longer the time elapsed since registration should be achieved by INGOs, it indicates that it took longer time for them to seek the content of both the PSU and Public Security Bureaus to be their supervisions or regulators and grant them legal identity.

@@

We use multilevel Bayesian modeling to analyze the empirical data.
